Generative Adversarial Networks

### 2017-12-06 cs6735/assignment/report.tex
finished DT

The algorithm begins at the root node with a set of catigorical, labled data $S$.

\subsection{Naïve Bayes}
\subsection{Adaboost}
\subsection{Random Forest}
\subsection{K-Nearest Neighbors}

>>>>

The algorithm as described by Mitchell \cite{Mitchell:1997:ML:541177} was implmented. The operations begin at the root node with a set of catigorical, labled data $S$. The attribute $A$ which introduces the largest information gain is chosen to split on. This is an exhaustive process which checks all remaining attributes. This process imediatly stops if there are no possible subsets (identical samples have same class label) or the split is not statistically significant (positive information gain). If these stopping conditions are not met, the data $S$ is split using attribute $A$ into subsets ${S1,...,SN}$ where $N$ is the amount of different categories of attribute $A$. A new node is then created for each subset. If the entropy of a new node is $0$ or the sample count is $1$, then the node is turned into a leaf and the splitting operation ends. Furthermore, two additional early stopping conditions are implemented. Max tree level and minimum number of samples attributes are initially set at the start of training.

After the initial ID3 algorithm was implemented, furthure enhancements were made to allow for continuous data to be used. This enhancement was taken from the C4.5  as developed by Ross Quinlan \citep{c45algorithm}. Given a continuous attribute $A$, we temporarily sort the data $S$. After the data is sorted, we iteratively determine a threshhold to split the data as the maximize the information gain. To test potential threshholds, we find two sequential numbers which are not of the same category and split at the midway point of the two values. This enhancements saves an a large amount of time for each continuous attribute found within the datasets as descritization does not need to occur. Furthermore, this algorithm chooses the optimal threshhold to split the data which improves classification accuracy.

\subsection{Naïve Bayes}
The Naive Bayes algorithm is implemented as described in \cite{Mitchell:1997:ML:541177}. This algorithm is named due its assumption of conditional independance amougst each attribute.

\hat{y}= \underset{k\;\in\;\{1,..K\}} {\mathrm{argmax}} \;\;P(C_k)\prod_{i=1}^mp\left(x_i\;|\;C_k\right)\prod_{j=m}^nP\left(x_j\;|\;C_k\right)\;\;?

\subsection{Adaboost}
\subsection{Random Forest}
\subsection{K-Nearest Neighbors}
